---
title: "Financial Time-Series Analysis, Risk Management and High-Frequency"
author: "Fotso Tenku"
date: "8 7 2020"
output: html_document
---

## 1-Introduction to Time-Series Analysis

## Question 1.1)

```{r}
set.seed(6822651)

CBK=read.csv("CBK.DE.csv")

# Example of the stationary times series (Plot of the Times Series of Commerzbank)
n=dim(CBK)[1]
time1= seq(2015, 2020+5/12, length.out = dim(CBK)[1])
plot(time1, CBK$Close, type= "l", ylab = "Closing Price", xlab = "Year", main = "Closing Price of Commerzbank 2015-2020")
```

## Example of the sationary times series (Plot of Return of the Commerzbank)

```{r}
close_CBK  = CBK$Close
return_CBK= diff(log(close_CBK))
time2<-time1[2:n]
plot(time2,return_CBK,type="l",xlab="Year",ylab = "Return CBK")
title("The Return Series of Commerzbank")
```

## Fit and Similation of a AR(2) with 400 observation of commerzbank'data

```{r}
set.seed(6822651)
n1=400
AR=arima(return_CBK, order =c(2, 0, 0))
AR
```

## Simulation of the fitted AR(2)-model

```{r}
AR_s=arima.sim(n1, model=list(ar=c(0.0262, 0.0073))) # This model is stationary

#Plot the fitted AR(2)-Model: AR(2): X(t)= 0.0262X(t-1) + 0.0073X(t-2) + err(t)
plot(AR_s, type="l", xlab="time", ylab="values", main = "Stationary AR(2) ")
```

## Example of Simation of non sationary AR(2)-process 

```{r}
AR_n=arima.sim(n1, model=list(ar=c(0.91, -0.34))) #non-stationary AR(2)-Process:X(t)= -0.91X(t-1) + 0.34 X(t-2) + err(t)

AR_s=arima.sim(n1, model=list(ar=c(0.0262, 0.0073)))

AR_n= 1:n1*0
AR_n
AR_n[1:2]= AR_s[1:2]
AR_n
for(t in 3:n1)
{
  AR_n[t]= 0.0262*AR_n[t-1] + 0.0073*AR_n[t-2] + rnorm(1)
}
```

## Plot Stionary and non Stationary AR(2)-Process

```{r}
plot(AR_n, type="l", xlab="time", ylab="values", main = "Stationary and non Stationary AR(2)")
lines(AR_s, col="red")
legend(x=40, y=-0.5, legend = c("nonstationary", "stationary"), col=c("black", "red"),lty = 1)
```

## Question 1.2-b)

```{r}
beer=read.csv("ausbeer.csv")

# State the model
n2=dim(beer)[1]
time.beer= seq(1956, 2010+3/12, length.out = n2)
plot(time.beer, beer$value, type= "l", ylab = "value", xlab = "time", main = "Quarterly Australian Beer production")

Return.beer<- diff(log(beer$value))
plot(time.beer[2:n2],Return.beer, type="l",xlab="time",ylab = "value", main = "Return beer Production")
```

## Find the best Model using AIC or BIC

```{r}
BIC = AIC =matrix(0, nrow = 3, ncol = 3)
for (p in 0:2)
{
  for (q in 0:2) 
    {
    model =arima(Return.beer, order =c(p, 0, q))
    AIC[p+1, q+1] = model$aic
    BIC[p+1, q+1] = -2*model$loglik+ log(n)*(p+q)
  }
  
}

AIC
min(AIC)
which(AIC==min(AIC))

best_model.AIC=arima(Return.beer, order = c(2, 0, 2))

best_model.AIC

#best_model.BIC=arima(ARMA, order = c(2, 0, 2))
```

## Check for invertibility and stationary of the model.

```{r}
ARMA=arima.sim(n=n2, model= list(ar=c(-0.0267, -0.8974), ma=c(-1.0551, 0.6951)))
plot(ARMA, type="l", xlab="time", ylab="value", main="ARMA(2,0,2)")
```

## 2-Financial Time-Series

```{r}
library(fGarch)

AAPL = read.csv("AAPL.csv")

n = dim(AAPL)[1]
R = diff(log(AAPL$Close))

# Fit the simple GARCH model
garchFit(~garch(1, 1), R, trace = FALSE)@fit$ics[2] # best model
garchFit(~garch(1, 2), R, trace = FALSE)@fit$ics[2]
garchFit(~garch(2, 1), R, trace = FALSE)@fit$ics[2]
garchFit(~garch(2, 2), R, trace = FALSE)@fit$ics[2]

GARCH = garchFit(~garch(1, 1), R, trace = FALSE) 
GARCH@fit$coef

# Fit the APPARCH model
garchFit(~aparch(1, 1), R, trace = FALSE)@fit$ics[2]# best model
garchFit(~aparch(1, 2), R, trace = FALSE)@fit$ics[2]
garchFit(~aparch(2, 1), R, trace = FALSE)@fit$ics[2]
garchFit(~aparch(2, 2), R, trace = FALSE)@fit$ics[2]

APARCH = garchFit(~aparch(1, 1), R, trace = FALSE)
APARCH@fit$coef
```

## Plot of the volatility of the GARCH(1,1)

```{r}
time = seq(2018, 2020, length.out = n)
Year = time[2:n]
plot(Year, GARCH@sigma.t, type = "l", ylab = "Volatility", main = "GARCH Model")
```

## plot of the GARCH by the APPARCH(1,1) extension

```{r}
plot(Year, GARCH@sigma.t, type = "l", ylab = "volatility",)
lines(Year, APARCH@sigma.t, col = "red")
title("Estimated volatility by APPARCH extension (AAPL)")
legend(y = 0.09, x = 2018.0, legend = c("GARCH", "APPARCH"), col = c("black", "red"), lty = 1)
```

```{r}
# calculate the VaR and the ES alpha = 0.025
# estimate GARCH(1,1)
GARCH = garchFit(~garch(1,1), R, trace = FALSE)
sigma_n = GARCH@sigma.t

#define the sequences. 
Year = seq(2018, 2020, length.out = n)
time = Year[2:n]

# calculate VaR and ES
VaR_n975 = qnorm(0.975) * sigma_n
ES_n975 = dnorm(qnorm(0.975))/(1 - 0.975) * sigma_n
```

## 3- Risk Management
 
```{r}
# find the time_series

set.seed(6810782)
DAI <- read.csv("DAI.DE.csv")
SAP<- read.csv("SAP.DE.csv")
DPW <- read.csv("DPW.DE.csv")
DTE <- read.csv("DTE.DE.csv")

#Display Stock price
n<-dim(DAI)[1]

time = seq(2015 + 4/12, 2018 + 4/12 , length.out = n)
par(mfrow=c(2,2))

plot(time,DAI$Close,type="l",xlab="Year",ylab="Price",main="The Daimler Index from 2015 to 2018")

plot(time,SAP$Close,type="l",xlab="Year",ylab="Price",main="The SAP Index from 2015 to 2018")

plot(time,DPW$Close,type="l",xlab="Year",ylab="Price",main="The DPW Index from 2015 to 2018")

plot(time,DTE$Close,type="l",xlab="Year",ylab="Price",main="The DTE Index from 2005 to 2018")
```

## Compute Return

```{r}
Return_DAI<-diff(log(DAI$Close))
Return_SAP<-diff(log(SAP$Close))
Return_DPW<-diff(log(DPW$Close))
Return_DTE<-diff(log(DTE$Close))

# Display Return

time2=time[2:n]
par(mfrow=c(2,2))
plot(time2,Return_DAI,type="l",xlab="Year",ylab = "Return")
title("The Return Series of DAI")

plot(time2,Return_SAP,type="l",xlab="Year",ylab = "Return")
title("The Return Series of SAP")

plot(time2,Return_DPW,type="l",xlab="Year",ylab = "Return")
title("The Return Series of DPW")

plot(time2,Return_DTE,type="l",xlab="Year",ylab = "Return")
title("The Return Series of DTE")
```

## Fit 4 GARCH(p,q) models for p, q = 1, 2

```{r}
library(fGarch)

# DAI
garchFit(~garch(1,1), Return_DAI, trace=FALSE)@fit$ics[2] # smallest BIC
garchFit(~garch(1,2), Return_DAI, trace=FALSE)@fit$ics[2]
garchFit(~garch(2,1), Return_DAI, trace=FALSE)@fit$ics[2]
garchFit(~garch(2,2), Return_DAI, trace=FALSE)@fit$ics[2]



# the best Model IS GARCH(1,1)

GARCH_DAI<- garchFit(~garch(1,1), Return_DAI, trace=FALSE)
GARCH_DAI@fit$coef

#SAP
garchFit(~garch(1,1), Return_SAP, trace=FALSE)@fit$ics[2]# smallest BIC
garchFit(~garch(1,2), Return_SAP, trace=FALSE)@fit$ics[2]
garchFit(~garch(2,1), Return_SAP, trace=FALSE)@fit$ics[2]
garchFit(~garch(2,2), Return_SAP, trace=FALSE)@fit$ics[2]


# Best Model IS GARCH(1,1)

GARCH_SAP <- garchFit(~garch(1,1), Return_SAP, trace=FALSE)
GARCH_SAP@fit$coef

#DPW
garchFit(~garch(1,1), Return_DPW, trace=FALSE)@fit$ics[2] # smallest BIC
garchFit(~garch(1,2), Return_DPW, trace=FALSE)@fit$ics[2]
garchFit(~garch(2,1), Return_DPW, trace=FALSE)@fit$ics[2]
garchFit(~garch(2,2), Return_DPW, trace=FALSE)@fit$ics[2]


# the best Model IS GARCH(1,1)

GARCH_DPW<- garchFit(~garch(1,1), Return_DPW, trace=FALSE)
GARCH_DPW@fit$coef

#DTE
garchFit(~garch(1,1), Return_DTE, trace=FALSE)@fit$ics[2] # smallest BIC
garchFit(~garch(1,2), Return_DTE, trace=FALSE)@fit$ics[2]
garchFit(~garch(2,1), Return_DTE, trace=FALSE)@fit$ics[2]
garchFit(~garch(2,2), Return_DTE, trace=FALSE)@fit$ics[2]



# the best Model IS GARCH(1,1)

GARCH_DTE<- garchFit(~garch(1,1), Return_DTE, trace=FALSE)
GARCH_DTE@fit$coef
```

## APARCH

```{r}
# DAI
garchFit(~aparch(1,1), Return_DAI, trace=FALSE)@fit$ics[2] # smallest BIC
garchFit(~aparch(1,2), Return_DAI, trace=FALSE)@fit$ics[2]
garchFit(~aparch(2,1), Return_DAI, trace=FALSE)@fit$ics[2]
garchFit(~aparch(2,2), Return_DAI, trace=FALSE)@fit$ics[2]

#the best Model IS APARCH(1,1)

APARCH_DAI<- garchFit(~aparch(1,1), Return_DAI, trace=FALSE)
APARCH_DAI@fit$coef

#SAP
garchFit(~aparch(1,1), Return_SAP, trace=FALSE)@fit$ics[2]# smallest BIC
garchFit(~aparch(1,2), Return_SAP, trace=FALSE)@fit$ics[2]
garchFit(~aparch(2,1), Return_SAP, trace=FALSE)@fit$ics[2]
garchFit(~aparch(2,2), Return_SAP, trace=FALSE)@fit$ics[2]

#the best Model IS APARCH(1,1)

APARCH_SAP<- garchFit(~aparch(1,1), Return_SAP, trace=FALSE)
APARCH_SAP@fit$coef

#DPW
garchFit(~aparch(1,1), Return_DPW, trace=FALSE)@fit$ics[2] # smallest BIC
garchFit(~aparch(1,2), Return_DPW, trace=FALSE)@fit$ics[2]
garchFit(~aparch(2,1), Return_DPW, trace=FALSE)@fit$ics[2]
garchFit(~aparch(2,2), Return_DPW, trace=FALSE)@fit$ics[2]

# the best Model IS APARCH(1,1)

APARCH_DPW<- garchFit(~aparch(1,1), Return_DPW, trace=FALSE)
APARCH_DPW@fit$coef

#DTE
garchFit(~aparch(1,1), Return_DTE, trace=FALSE)@fit$ics[2]
garchFit(~aparch(1,2), Return_DTE, trace=FALSE)@fit$ics[2] # smallest BIC
garchFit(~aparch(2,1), Return_DTE, trace=FALSE)@fit$ics[2]
garchFit(~aparch(2,2), Return_DTE, trace=FALSE)@fit$ics[2]

# the best Model IS APARCH(1,2)

APARCH_DTE<- garchFit(~aparch(1,2), Return_DTE, trace=FALSE)
APARCH_DTE@fit$coef


#Calculate the 0.95 VaR and ES for both models and all companies

#DAI

#GARCH

sigma_GARCH_DAI<-GARCH_DAI@sigma.t
VaR_GARCH_DAI95 = qnorm(0.95) * sigma_GARCH_DAI
ES_GARCH_DAI95 = dnorm(qnorm(0.95))/(1 - 0.95) * sigma_GARCH_DAI
```

## APARCH

```{r}
sigma_APARCH_DAI<-APARCH_DAI@sigma.t
VaR_APARCH_DAI95 = qnorm(0.95) * sigma_APARCH_DAI
ES_APARCH_DAI95 = dnorm(qnorm(0.95))/(1 - 0.95) * sigma_APARCH_DAI

#plot

par(mfrow = c(2, 1), cex = 0.75, xpd = NA)

plot(time2,Return_DAI,type="l",xlab="Year",ylab = "Return")
title("The Return Series and 95% VAR, ES (GARCH) of DAI")
lines(time2, VaR_GARCH_DAI95, col = 2)
lines(time2, ES_GARCH_DAI95, col = 4)

plot(time2,Return_DAI,type="l",xlab="Year",ylab = "Return")
title("The Return Series and 95% VAR, ES (APARCH) of DAI")
lines(time2, VaR_APARCH_DAI95, col = 2)
lines(time2, ES_APARCH_DAI95, col = 4)

legend(y = -0.14, x = 2017, legend = c("Return", "VaR", "ES"),
       col = c(1, 2, 4), lwd = 1, horiz = TRUE)
```

```{r}
#SAP

#GARH

sigma_GARCH_SAP<-GARCH_SAP@sigma.t
VaR_GARCH_SAP95 = qnorm(0.95) * sigma_GARCH_SAP
ES_GARCH_SAP95 = dnorm(qnorm(0.95))/(1 - 0.95) * sigma_GARCH_SAP

#APARCH

sigma_APARCH_SAP<-APARCH_SAP@sigma.t
VaR_APARCH_SAP95 = qnorm(0.95) * sigma_APARCH_SAP
ES_APARCH_SAP95 = dnorm(qnorm(0.95))/(1 - 0.95) * sigma_APARCH_SAP

# Plot

par(mfrow = c(2, 1), cex = 0.75, xpd = NA)

plot(time2,Return_SAP,type="l",xlab="Year",ylab = "Return")
title("The Return Series and 95% VAR, ES (GARCH) of SAP")
lines(time2, VaR_GARCH_SAP95, col = 2)
lines(time2, ES_GARCH_SAP95, col = 4)

plot(time2,Return_SAP,type="l",xlab="Year",ylab = "Return")
title("The Return Series and 95% VAR, ES (APARCH) of SAP")
lines(time2, VaR_APARCH_SAP95, col = 2)
lines(time2, ES_APARCH_SAP95, col = 4)

legend(y = -0.11, x = 2017, legend = c("Return", "VaR", "ES"),
       col = c(1, 2, 4), lwd = 1, horiz = TRUE)
```

```{r}
#DPW

#GARCH

sigma_GARCH_DPW<-GARCH_DPW@sigma.t
VaR_GARCH_DPW95 = qnorm(0.95) * sigma_GARCH_DPW
ES_GARCH_DPW95 = dnorm(qnorm(0.95))/(1 - 0.95) * sigma_GARCH_DPW

#APARCH

sigma_APARCH_DPW<-APARCH_DPW@sigma.t
VaR_APARCH_DPW95 = qnorm(0.95) * sigma_APARCH_DPW
ES_APARCH_DPW95 = dnorm(qnorm(0.95))/(1 - 0.95) * sigma_APARCH_DPW

#Plot

par(mfrow = c(2, 1), cex = 0.75, xpd = NA)

plot(time2,Return_DPW,type="l",xlab="Year",ylab = "Return")
title("The Return Series and 95% VAR, ES (GARCH) of DPW")
lines(time2, VaR_GARCH_DPW95, col = 2)
lines(time2, ES_GARCH_DPW95, col = 4)

plot(time2,Return_DPW,type="l",xlab="Year",ylab = "Return")
title("The Return Series and 95% VAR, ES (APARCH) of DPW")
lines(time2, VaR_APARCH_DPW95, col = 2)
lines(time2, ES_APARCH_DPW95, col = 4)

legend(y = -0.12, x = 2017, legend = c("Return", "VaR", "ES"),
       col = c(1, 2, 4), lwd = 1, horiz = TRUE)
```

```{r}
# DTE
#GARCH

sigma_GARCH_DTE<-GARCH_DTE@sigma.t
VaR_GARCH_DTE95 = qnorm(0.95) * sigma_GARCH_DTE
ES_GARCH_DTE95 = dnorm(qnorm(0.95))/(1 - 0.95) * sigma_GARCH_DTE


#APARCH

sigma_APARCH_DTE<-APARCH_DTE@sigma.t
VaR_APARCH_DTE95 = qnorm(0.95) * sigma_APARCH_DTE
ES_APARCH_DTE95 = dnorm(qnorm(0.95))/(1 - 0.95) * sigma_APARCH_DTE

#Plot

par(mfrow = c(2, 1), cex = 0.75, xpd = NA)

plot(time2,Return_DTE,type="l",xlab="Year",ylab = "Return")
title("The Return Series and 95% VAR, ES (GARCH) of DTE")
lines(time2, VaR_GARCH_DTE95, col = 2)
lines(time2, ES_GARCH_DTE95, col = 4)

plot(time2,Return_DTE,type="l",xlab="Year",ylab = "Return")
title("The Return Series and 95% VAR, ES (APARCH) of DTE")
lines(time2, VaR_APARCH_DTE95, col = 2)
lines(time2, ES_APARCH_DTE95, col = 4)

legend(y = -0.11, x = 2017, legend = c("Return", "VaR", "ES"),
       col = c(1, 2, 4), lwd = 1, horiz = TRUE)
```

```{r}
# GARCH and APARCH of DAIMLER
# DAI
#GARCH

garchFit(~garch(1,1), Return_DAI, trace=FALSE)@fit$coef
garchFit(~garch(1,2), Return_DAI, trace=FALSE)@fit$coef
garchFit(~garch(2,1), Return_DAI, trace=FALSE)@fit$coef
garchFit(~garch(2,2), Return_DAI, trace=FALSE)@fit$coef

# APARCH

garchFit(~aparch(1,1), Return_DAI, trace=FALSE)@fit$coef
garchFit(~aparch(1,2), Return_DAI, trace=FALSE)@fit$coef
garchFit(~aparch(2,1), Return_DAI, trace=FALSE)@fit$coef
garchFit(~aparch(2,2), Return_DAI, trace=FALSE)@fit$coef
```

## 4 High-Frequency Financial 

```{r}
set.seed(6810782)

HF_BMW<- read.csv("HF-BMW.csv",header = FALSE)

Data1<- HF_BMW[82,] 
Day_1<-unlist(Data1,recursive = TRUE,use.names=FALSE)

Data2<- HF_BMW[83,]
Day_2<- unlist(Data2,recursive = TRUE,use.names = FALSE)

Data3<- HF_BMW[84,]
Day_3<- unlist(Data3,recursive = TRUE,use.names = FALSE)

#Plot all three time-series


n <- length(Day_1)

X<-format(seq(as.POSIXct( "2020-08-22 09:00:00", tz="GMT"), length.out=n,  by='1 min'), '%H:%M')

par(mfrow = c(3, 1))

plot(Day_1,type="l",xaxt="n",xlab="time",ylab="Price",main="the BMW index of the day 1")
axis(1,at=1:511,labels =X[1:511])

plot(Day_2,type="l",xaxt="n",xlab="time",ylab="Price",main="the BMW index of the day 2")
axis(1,at=1:511,labels = X[1:511])

plot(Day_3,type="l",xaxt="n",xlab="time",ylab="Price",main="the BMW index of the day 3")
axis(1,at=1:511,labels = X[1:511])
```

```{r}
# Calculate the Return

Return_Day_1<- diff(log(Day_1))
Return_Day_2<- diff(log(Day_2))
Return_Day_3<- diff(log(Day_3))

# Plot the Return

par(mfrow=c(3,1))
plot(Return_Day_1,type="l",xaxt="n",xlab="time",ylab = "Return",main="The Return Series of BMW of the day 1")
axis(1,at=2:511,labels = X[2:511])

plot(Return_Day_2,type="l",xaxt="n",xlab="time",ylab = "Return",main="The Return Series of BMW of the day 2")
axis(1,at=2:511,labels = X[2:511])

plot(Return_Day_3,type="l",xaxt="n",xlab="time",ylab = "Return",main="The Return Series of BMW of the day 3")
axis(1,at=2:511,labels = X[2:511])
```

```{r}
# Calculate Volatility
library(fGarch)

Return_Day_1.GARCH11=garchFit(~garch(1,1), Return_Day_1, trace=FALSE)
volatility_Day_1<- Return_Day_1.GARCH11@sigma.t


Return_Day_2.GARCH11=garchFit(~garch(1,1), Return_Day_2, trace=FALSE)
volatility_Day_2 <- Return_Day_2.GARCH11@sigma.t

Return_Day_3.GARCH11=garchFit(~garch(1,1), Return_Day_3, trace=FALSE)
volatility_Day_3 <- Return_Day_3.GARCH11@sigma.t

data<-data.frame(volatility_Day_1,volatility_Day_2,volatility_Day_3)
head(data)

```

